Is this normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2025-01-31 paper.qmd
fig 6 fixed

# when drawing I want to add clustering information
labels <- data.frame(
  x = c(seq(1960, 2020, length.out = 7),
        as.numeric(names(X_km$cluster))),
  label = c(seq(1960, 2020, length.out = 7),
        paste0("\n",X_km$cluster))
)
cluster_df <- as_tibble(X_km$cluster, rownames = "year") %>%
  add_column(variable = "num_precp_01")
p <- plot(weather_SCD_rescaled, type = "cell", n_digits = 0, continuous_rowname = 10, rotate_x = FALSE) +
  geom_text(data = cluster_df,
            mapping = aes(x = as.numeric(year),
                               y = variable, label = value,
                          color = as.factor(value)),
            size = 3, fontface = "bold",
            inherit.aes = F) +
  scale_color_manual(values = c("#201158", "#005260", "#007C46", "#999600", "#F9A391"),
                     guide = "none") +
  theme(
    #legend.position = "none",
        aspect.ratio = 0.5,
        text = element_text(size = 10)) +
  scale_x_continuous(breaks = seq(1960, 2020, 5),
                     labels = c(as.character(seq(60, 95, 5)),
                                "00", "05",
                                as.character(seq(10, 20, 5))))
ggsave("images/weather3.png", p, "png", bg = "white",
       width = 6, height = 3)
```

>>>>

# when drawing I want to add clustering information
labels <- data.frame(
  x = c(seq(1960, 2020, length.out = 7),
        as.numeric(names(X_km$cluster))),
  label = c(seq(1960, 2020, length.out = 7),
        paste0("\n",X_km$cluster))
)
cluster_df <- as_tibble(X_km$cluster, rownames = "year") %>%
  add_column(variable = "num_precp_01")
colnames(weather_SCD_rescaled$phi) <-
  c("atmax", "atmin", 
         "nsumm",
         "nheat", "p",
         "sunh",
         "nclear",
         "ncloud",
         "rh",
         "rhmax" ,
         "rhmin",
         "vwind",
         "vw60",
         "vwmax",
         "prec",
         "nprec")
cluster_df$variable <- "nprec"
p <- plot(weather_SCD_rescaled, type = "cell", n_digits = 0, continuous_rowname = 10, rotate_x = FALSE) +
  geom_text(data = cluster_df,
            mapping = aes(x = as.numeric(year),
                               y = variable, label = value,
                          color = as.factor(value)),
            size = 3, fontface = "bold",
            inherit.aes = F) +
  scale_color_manual(values = c("#040404", "#55125D", "#A01975", "#E45358", "#F7AA2D"),
                       #c("#201158", "#005260", "#007C46", "#999600", "#F9A391"),
                     guide = "none") +
  theme(
    #legend.position = "none",
        aspect.ratio = 0.5,
        text = element_text(size = 10)) +
  scale_x_continuous(breaks = seq(1960, 2020, 5),
                     labels = c(as.character(seq(60, 95, 5)),
                                "00", "05",
                                as.character(seq(10, 20, 5))))
ggsave("images/weather3.png", p, "png", bg = "white",
       width = 6, height = 3)
```
